---
title: "Simulation with Python Experiment Data (Contextual)"
date: "`r Sys.Date()`"
output: pdf_document
fontsize: 10pt
---

# 1. Preparing the data
```{r setup}
library(reticulate)
library(banditsCI)

# Read in data generated in python notebook

gammahat <- as.matrix(read.csv('gammahat.csv', header = FALSE))
muxs <- as.matrix(read.csv('muxs.csv', header = FALSE))

# probabilities
np <- import("numpy")
# 3 dimensions: time, contexts, treatment arms
probs_array <- np$load("probs.npy") 


# Define the policies we want to evaluate
policy1_main <- list(
  # includes all matrices in policy1 and policy0
  matrix(
    c(rep(1, nrow(gammahat)), 
      rep(0, nrow(gammahat)), 
      rep(0, nrow(gammahat)),  
      rep(0, nrow(gammahat))),
    nrow = nrow(gammahat)),
  matrix(
    c(rep(0, nrow(gammahat)), 
      rep(1, nrow(gammahat)), 
      rep(0, nrow(gammahat)), 
      rep(0, nrow(gammahat))),
    nrow = nrow(gammahat)),
  matrix(
    c(rep(0, nrow(gammahat)), 
      rep(0, nrow(gammahat)), 
      rep(1, nrow(gammahat)), 
      rep(0, nrow(gammahat))),
    nrow = nrow(gammahat)),
  matrix(
    c(rep(0, nrow(gammahat)), 
      rep(0, nrow(gammahat)), 
      rep(0, nrow(gammahat)), 
      rep(1, nrow(gammahat))),
    nrow = nrow(gammahat)))
```

# 2. Estimation

## 2.1 Main Effects
```{r main_effects}
best_mtx <- matrix(0, nrow = nrow(gammahat), ncol = ncol(gammahat))
best_mtx[, which.max(colMeans(muxs))] <- 1

output_estimates_best <- output_estimates(policy1 = list(best_mtx),
                                          gammahat = gammahat,
                                          probs_array = probs_array,
                                          floor_decay = 0.8)

uniform_var <- estimate(0:(nrow(gammahat)-1),
                        gammahat, 
                        best_mtx)
output_estimates_best[[1]] <- rbind(output_estimates_best[[1]],
                                    'uniform_var' = c(uniform_var['estimate'],
                                                      sqrt(uniform_var['var'])))


optimal_mtx <- matrix(0, nrow = nrow(gammahat), ncol = ncol(gammahat))
optimal_mtx[cbind(1:nrow(gammahat), apply(muxs, 1, which.max))] <- 1

output_estimates_optimal <- output_estimates(policy1 = list(optimal_mtx),
                                             gammahat = gammahat,
                                             probs_array = probs_array,
                                             floor_decay = 0.8)

uniform_var <- estimate(0:(nrow(gammahat)-1),
                        gammahat, 
                        optimal_mtx)
output_estimates_optimal[[1]] <- rbind(output_estimates_optimal[[1]],
                                       'uniform_var' = c(
                                         uniform_var['estimate'], 
                                         sqrt(uniform_var['var'])))

```

## 2.2 Treatment effects in contrast to control
$\delta(w_1, w_2) = E[Y_t(w_1) - Y_t(w_2)]$.

The first approach: use the difference in AIPW scores as the unbiased scoring rule for $\delta (w_1, w_2)$.

The following function implements the first approach by subtracting policy0, the control arm, from all the arms in policy1, except for the control arm itself.

```{r contrasts_1}
out_full_te1 <- output_estimates(
  policy0 = best_mtx,
  policy1 = list(optimal_mtx),
  contrasts = "combined",
  gammahat = gammahat,
  probs_array = probs_array,
  floor_decay = 0.8)

uniform_var <- estimate(0:(nrow(gammahat)-1),
                        gammahat, 
                        optimal_mtx-best_mtx)
out_full_te1[[1]] <- rbind(out_full_te1[[1]],
                           'uniform_var' = c(
                             uniform_var['estimate'], 
                             sqrt(uniform_var['var'])))
```

The second approach takes asymptotically normal inference about $\delta(w_1, w_2): \delta ^ hat (w_1, w_2) = Q ^ hat (w_1) - Q ^ hat (w_2)$

```{r contrasts_2}

out_full_te2 <- output_estimates(
  policy0 = best_mtx,
  policy1 = list(optimal_mtx),
  contrasts = "separate",
  gammahat = gammahat,
  probs_array = probs_array,
  floor_decay = 0.8)

out_full_te1[[1]] <- rbind(out_full_te1[[1]],
                           'uniform_var' = c(
                             output_estimates_optimal[[1]]['uniform_var','estimate'] - output_estimates_best[[1]]['uniform_var','estimate'], 
                             sqrt(output_estimates_optimal[[1]]['uniform_var','std.error']^2 + 
                                    output_estimates_best[[1]]['uniform_var','std.error']^2)
                           ))
```

# 3. Compare the results
```{r results}
# Compare the two approaches for uniform and non_contextual_two_point
comparison_df <- data.frame(method = character(),
                            estimate = numeric(),
                            std_error = numeric(),
                            var = numeric(),
                            contrasts = character(),
                            policy = integer(),
                            stringsAsFactors = FALSE)

# Function to process and append data
process_data <- function(data, policy_num, contrasts) {
  for (method in c("non_contextual_minvar", "contextual_minvar",
                   "non_contextual_stablevar", "contextual_stablevar", 
                   "uniform_var")) {
    if (method %in% rownames(data)) {
      row <- data.frame(
        method = method,
        estimate = data[method, "estimate"],
        std_error = data[method, "std.error"],
        var = data[method, "std.error"]^2,
        contrasts = contrasts,
        policy = policy_num,
        stringsAsFactors = FALSE
      )
      comparison_df <<- rbind(comparison_df, row)
    }
  }
}

# Process and append data for each subset and condition
process_data(output_estimates_best[[1]], "best", "main effect")
process_data(output_estimates_optimal[[1]], "optimal", "main effect")
process_data(out_full_te1[[1]], "(best,optimal)", "combined")
process_data(out_full_te2[[1]], "(best,optimal)", "separate")


comparison_df <- comparison_df[order(comparison_df$policy, decreasing = TRUE), ]

# print the comparison data frame as a table
knitr::kable(comparison_df)
```

